Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-18 main.tex
Policies

Informally, a (micro-){\em policy} is an enriched step function that,
whenever is is defined, agrees with $\stepstounderfull$.  It represents an
enforcement mechanism that sometimes halts programs earlier than the bare
step relation does but that agrees with the bare step relation as long as it
allows evaluation to proceed.  We write
$(\contour_1,\mach_1) \stepstounder{\pol} (\contour_2,\mach_2)$ for
$\pol(\contour_1,\mach_1) = (\contour_2,\mach_2)$.

>>>>

\leo{I think with the property being just a (special) hyperproperty
  again, the policy can be ``more detailed'' - including low-level
  enforcement details like tags, etc. But you should always be able to
  reconstruct the contoured trace given an initial contour and an
  initial state. I'm taking that approach here:}

Formally, a policy
%
$\pol \in \exists X.\; (\CONTOURS \times \MACHS \rightarrow X)
                       \times (X \rightarrow \CONTOURS)
                       \times (\MACHS \times X \rightharpoonup \MACHS \times X)$
%
comprises
\begin{enumerate*}
  \item a private type $X$ corresponding to an ``implementation'' of the contour,
  \item an initializer: a function taking a contour and a machine state to an initial value of $X$,
  \item a projection: a way of reading a contour out of the private type,
  \item a partial step function of type $(\MACHS \times X) \rightharpoonup X$
    that, when defined, defines the private state after a step of the machine
    (based on the $\stepstounderfull$ relation)
\end{enumerate*}
That is, a policy takes a starting contour and produces a runtime monitor
that carries along some private information and uses it to decide whether to
terminate execution early.

\leo{Example? how detailed?}  For example, for standard
lockstep-noninterference with only two secrecy levels, the private
state {\em is} the contour.

A policy $\pol$ {\em guarantees} property $\prop$ if for every pair of
states $M$ and $M'$ and for every starting contour $C$, the pair of
contoured traces that you get from the policy is in the property.

\leo{New attempt ends here}
Informally, a (micro-){\em policy} is an enriched step function that,
whenever is is defined, agrees with $\stepstounderfull$.  It represents an
enforcement mechanism that sometimes halts programs earlier than the bare
step relation does but that agrees with the bare step relation as long as it
allows evaluation to proceed.  We write
$(\contour_1,\mach_1) \stepstounder{\pol} (\contour_2,\mach_2)$ for
$\pol(\contour_1,\mach_1) = (\contour_2,\mach_2)$.
